---
title: "BBall Season Presentation"
author: "Sam Eckhardt and Joey Miranda"
date: "Sunday, October 05, 2014"
output: pdf_document
---
```{r}

library(XML)
library(ggmap)
library(ggplot2)
library(dplyr)



```


## The Data 

The Data we have has been recieved from espn.com. It inclu?get_mapdes the season statistics for two conferences, the Big 12 and the West Coast Conference, from the season of 2001-2002 to the season of 2012-2013. 


##Location of Teams With Points in Team Color

```{r}

# Where exactly are these cities on the US map? Let's plot the cities of these teams
  
location=c(-125,24.207,-70,50) # It took a bit to figure these coordinates out - zoom to the appropriate location and level using openstreetmap.org 
# and find coordinates from the export link

map=get_map(location=location,maptype="roadmap",source="google")
usmap=ggmap(map)
locs=geocode(as.character(unique(Gamestatistics$City)))
locs$City=unique(Gamestatistics$City) 
Gamestatistics$lat=locs$lat[ match(Gamestatistics$City,locs$City)]# bring latitude and longitude information to main data frame
Gamestatistics$lon=locs$lon[ match(Gamestatistics$City,locs$City)]
 
levels(Gamestatistics$Team) # note the sequence of teams and arrange the colors in palette in corresponding sequence

 # The plot
teampalette <- c("#006600","#FFFFFF","#000099","#990000","#0000FF","#6600CC","#990033","#660000","#FF3300","#FF6633","#99CCFF","#330099","#99CC66","#00CCFF","#009900","#999999","#6633CC","#FF9933","#FF0000", "#FFFF00")


usmap+geom_point(data=Gamestatistics,aes(x=lon,y=lat,color=Team),size=7)+ ggtitle("Location of WCC and Big 12 Schools")+
  scale_color_manual(values=teampalette) # add theme(legend.position="none") if you don't want the legend


```


## Average Points Per Game of Players by Conference in Different Seasons

```{r}
ppgmean=Gamestatistics %>% group_by(Team,Year) %>% summarise(Mean.Points.Per.Game=mean(Points.Per.Game))

teampalette <- c("#006600","#FFFFFF","#000099","#990000","#0000FF","#6600CC","#990033","#660000","#FF3300","#FF6633","#99CCFF","#330099","#99CC66","#00CCFF","#009900","#999999","#6633CC","#FF9933","#FF0000", "#FFFF00")

levels(Gamestatistics$Team)
#Plot
ggplot(ppgmean,aes(x=Year,y=Mean.Points.Per.Game,,color=Team,group=Team))+
  geom_point()+geom_line()+
  theme(axis.text.x = element_text(angle=-90))+ggtitle("Mean Points Per Game of Players of Different Teams in Different Seasons") +scale_color_manual(values=teampalette)

```

## Average Points Per Game of Players by WCC Teams in Different Seasons

```{r}
ppgmeanConf=Gamestatistics %>% group_by(Team,Year) %>% summarise(Mean.Points.Per.Game=mean(Points.Per.Game))

teampaletteWCC <- c("#FFFFFF","#000099","#990033","#FF6633","#99CCFF","#330099","#99CC66","#00CCFF","#009900","#999999")

levels(Gamestatistics$Team)

ggplot(subset(ppgmeanConf,Team %in% c("Gonzaga Bulldogs","Brigham Young Cougars","Loyola Marymount Lions","Saint Mary's Gaels","San Francisco Dons", "Pepperdine Waves", "Pacific Tigers","San Diego Toreros","Portland Pilots","Santa Clara Broncos","")),aes(x=Year,y=Mean.Points.Per.Game,color=Team,group=Team))+geom_point()+geom_line()+ggtitle("Mean Points Per Game of Players in the West Coast Conference by Season")+scale_color_manual(values=teampaletteWCC)
```

##Average Points Per Game of Players by Big 12 Teams in Different Seasons

```{r}
ppgmeanConf=Gamestatistics %>% group_by(Team,Year) %>% summarise(Mean.Points.Per.Game=mean(Points.Per.Game))

teampaletteB12 <- c("#006600","#990000","#0000FF","#6600CC","#660000","#FF3300","#6633CC","#FF9933","#FF0000", "#FFFF00")

levels(Gamestatistics$Team)

ggplot(subset(ppgmeanConf,Team %in% c("Baylor Bears","Kansas Jayhawks","Kansas State Wildcats","Oklahoma Sooners","Oklahoma State Cowboys", "Texas Tech Red Raiders", "TCU Horned Frogs","Texas Longhorns","West Virginia Mountaineers","Iowa State Cyclones","")),aes(x=Year,y=Mean.Points.Per.Game,color=Team,group=Team))+geom_point()+geom_line()+ggtitle("Mean Points Per Game of Players in the Big 12 by Season")+scale_color_manual(values=teampaletteB12)
```

